---
title: "p8105_hw6_js5165"
author: "Jingqi Song"
date: "November 28, 2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(psych)
library(modelr)
theme_set(theme_bw())
```

## Problem 1

### Read and tidy data

```{r p1_1}
homicide = read_csv('./homicide-data.csv') %>% 
  janitor::clean_names() %>% 
  mutate(city_state = paste(paste0(city, ","), state),
         victim_race = fct_relevel(ifelse(victim_race == 'White', 'white', 'non-white'), 'white'),
         victim_age = as.numeric(victim_age),
         victim_sex = as.factor(victim_sex),
         resolved = as.numeric(disposition == 'Closed by arrest')) %>% 
  filter(!city_state %in% c('Dallas, TX', 'Phoenix, AZ', 'Kansas City, MO', 'Tulsa, AL')) 

```

### Obtain the estimate and confidence interval for Baltimore

```{r p1_2}
baltimore_glm = homicide %>% 
  select(uid, victim_race, victim_age, victim_sex, city_state, resolved) %>% 
  filter(city_state == 'Baltimore, MD') %>% 
  glm(resolved ~ victim_age + victim_sex + victim_race, data =., family = binomial()) 

save(baltimore_glm, file = 'Baltimore_logistic.RData')

baltimore_glm %>% broom::tidy() %>% 
  mutate(OR = exp(estimate),
         conf_low = exp(estimate - 1.96*std.error),
         conf_high = exp(estimate + 1.96*std.error)) %>% 
  filter(term == 'victim_racenon-white') %>% 
  dplyr::select(term, estimate, OR, conf_low, conf_high, p.value) %>% 
  knitr::kable(digits = 3)
```

### Obtain the estimate and confidence interval for each city

```{r p1_3}
all_glm = function(x){
  homicide %>% 
  filter(city_state == x) %>% 
  glm(resolved ~ victim_age + victim_sex + victim_race, data =., family = binomial())  %>% 
  broom::tidy() %>% 
  mutate(OR = exp(estimate),
         conf_low = exp(estimate - 1.96*std.error),
         conf_high = exp(estimate + 1.96*std.error)) %>% 
    filter(term == 'victim_racenon-white') %>% 
    dplyr::select(beta = estimate, OR, conf_low, conf_high, p.value)
  }

city_glm = tibble(city_state = unique(homicide$city_state)) %>% 
  mutate(map(.x = unique(homicide$city_state), ~all_glm(.x))) %>% 
  unnest

```

### Plot that shows the estimated ORs and CIs for each city

```{r p1_4}
city_glm %>%
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) +
  geom_point() +
  geom_errorbar(mapping = aes(ymin = conf_low, ymax = conf_high)) + 
  labs(
    title = 'Estimate OR for Solving Homicides Comparing Non-white Victims to White Victims in Each City',
    x = 'City, State',
    y = 'Estimate OR'
    ) +
  theme(axis.text.x = element_text(angle = 90, size = 7),
        title = element_text(size = 9))

```

All the cities except Durham, Birmingham and Tampa, the estimate ratio are all lower than 1, which indicates the lower odds of solving homicides in non-white victims compared to in white victims. But we also need to consider about the 95% CI when giving our result.


## Problem 2

### Read and tidy data

```{r p2_1}
birthweight = read_csv('./birthweight.csv') %>% 
  janitor::clean_names() %>% 
  mutate(babysex = as.factor(babysex),
         frace = as.factor(frace),
         malform = as.factor(malform),
         mrace = as.factor(mrace))
describe(birthweight)

```

There is no missing data in the dataset. 
I am going to use step-wise selection, which is a data-driven model-building process.

### Selecting predictors for my model

```{r p2_2 stepwise}
full_model = lm(bwt ~ ., data = birthweight)
step(full_model, direction='both',trace = 0)
```

Then we got 11 predictors in our model: babysex, bhead, blength, delwt, fincome, gaweeks, mheight, mrace, parity, ppwt and smoken

Combining previous study result (G. LETAMO: FACTORS INFLUENCING LOW BIRTH WEIGHT AND PREMATURITY; Christopher S.: Maternal characteristics influencing birth weight and infant weight gain in the first 6 weeks post-partum), I chose 6 variables into my model: mother’s weight at delivery, mother’s race, gestational age in weeks, mother’s height, family monthly income, and average number of cigarettes smoked per day during pregnancy.

```{r p2_2 assumption}
model = lm(bwt ~ delwt + fincome + gaweeks + mheight + mrace + smoken, data = birthweight)
summary(model)

#check assumption
par(mfrow = c(2,2))
plot(model)
```

We can see that the normal Q-Q plot is linear, the assumption is not violated.

```{r p2_2 res_fit}
res_fit = birthweight %>% 
  add_predictions(model) %>% 
  add_residuals(model)
ggplot(res_fit, aes(x = pred, y = resid)) +
    geom_point() +
    labs(
      title = 'Residual vs. Fit',
      x = 'Prediction',
      y = 'Residual'
      )
```

We can see the residuls are clustered. The model still need to be refined.

### Model Comparison

```{r p2_3}
cv = birthweight %>% 
  crossv_mc(100)
cv_compare = cv %>% 
  mutate(model_1 = map(train, ~lm(bwt ~ blength + gaweeks, data = .)),
         model_2 = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead*babysex + bhead*blength + blength*babysex + bhead*babysex*blength, data = .)),
         model = map(train, ~lm(bwt ~ delwt + fincome + gaweeks + mheight + mrace + smoken, data = .)),
         rmse_model_1 = map2_dbl(model_1, test, ~rmse(.x, .y)),
         rmse_model_2 = map2_dbl(model_2, test, ~rmse(.x, .y)),
         rmse_model = map2_dbl(model, test, ~rmse(.x, .y)))
```

## Comparison Using Plot

```{r p2_4}
cv_compare %>% 
  select(starts_with('rmse')) %>% 
  gather(key = model, value = rmse, rmse_model_1:rmse_model) %>% 
  mutate(model = str_replace(model, 'rmse_', ""),
         model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin() + 
  labs(
    title = "Prediction error distribution for models",
    x = "Model",
    y = "RMSE"
   )
```

Based on the violin plot, model 2 has the smallest RMSE; I will choose this model to predict birth weight among the three.

